---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# easyplater

<!-- badges: start -->
<!-- badges: end -->

easyplater is a tool for generating microplate manifests while decoupling clinical data from plate location effects.

In short, easyplater is an easy to use algorithm for generating 96-well plate designs without confounding clinical variables with plate location effects. Simply input clinical data and user-assigned clinical variable weights, and easyplater outputs the most deconvolved plate design it finds in plain text and R Markdown formats.

## Installation

You can install the development version of `easyplater` from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("IMCM-OX/easyplater")
```

## Example usage

```{r example, warnings=FALSE}
library(easyplater)

# easyplater comes with a built-in example plate manifest
example_manifest

# Run easyplater in one step
easyplater_design <- make_easyplater_design(
  manifest_df = example_manifest,
  plateID = "plate 1",
  columns_for_scoring = c("Cohort","Group","Sex","AgeGroup"),
  column_weights = c(5, 5, 10, 4),
  cols_to_categorize = list(c("Age", 10, NULL, "AgeGroup")),
  imbalance_fixer = list(T, "Group", list("D1", "HC1", "D7", "D8"), 3),
  plate_size = 96
)

# Use a function exported from the OlinkAnalyze package to display plate layout
olink_displayPlateLayout(data = easyplater_design, fill.color = "Group", include.label = T)
```
